pema application

### 2022-11-28 paper/manuscript.Rmd
update 2022-11-28 13:44:48

author:
  - name: "Caspar J. Van Lissa"
    affiliation: "1,2"
    corresponding: yes
    address: "Padualaan 14, 3584CH Utrecht, The Netherlands"
    email: "c.j.vanlissa@uu.nl"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Formal Analysis
      - Funding acquisition
      - Methodology
      - Project administration
      - Software
      - Supervision
      - Writing – original draft
      - Writing – review & editing
  - name: "Sara van Erp"
    affiliation: "1"
    role:
      - Methodology
      - Software
      - Writing – original draft
      - Writing – review & editing
  - name: "Eli-Boaz Clapper"
    affiliation: "1"
    role:
      - Formal Analysis
      - Writing – original draft
      - Writing – review & editing
affiliation:
  - id            : "1"
    institution   : "Utrecht University, dept. Methodology & Statistics"
  - id            : "2"
    institution   : "Open Science Community Utrecht"

@@

abstract: |
  When meta-analyzing heterogeneous bodies of literature,
  meta-regression can be used to account for potentially relevant between-studies differences.
  A key challenge is that the number of these potential moderators is often high
  relative to the number of studies.
  This introduces a risk of overfitting and finding spurious results.
  To overcome this challenge,
  [we introduce Bayesian Regularized Meta-Analysis (BRMA),
  which selects relevant moderators from a larger set of candidates
  by shrinking small regression coefficients towards zero
  with regularizing (LASSO or horseshoe) priors.]{#lassoabstract}
  This method is suitable when there are many potential moderators,
  but it is not known beforehand which of them are relevant.
  A simulation study compared BRMA against state-of-the-art random effects
  meta-regression using restricted maximum likelihood (RMA).
  Results indicated that BRMA outperformed RMA on three metrics:
  BRMA had superior predictive performance, which means that the results
  generalized better;
  BRMA was better at rejecting irrelevant moderators,
  and worse at detecting true effects of relevant
  moderators,
  but the overall proportion of Type I and Type II errors was
  equivalent to RMA.
  BRMA regression coefficients were slightly biased towards zero (by design),
  but its residual heterogeneity estimates were less biased than those of RMA.
  BRMA performed well with as few as 20 studies,
  suggesting its suitability as a small sample solution. 
  We present free open source software implementations in the R-package `pema` (for penalized meta-analysis)
  and in the stand-alone statistical program JASP.
  An applied example demonstrates the use of the R-package.

@@

bibliography      : ["r-references.bib", "references.bib",
                     "sara-references.bib", "eli-references.bib", "metaforest.bib"]

@@

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed, warning = FALSE)
```

@@

<span id = "openingparagraph">A common application of meta-analysis is to summarize existing bodies of literature.
A crucial challenge is that there is often substantial heterogeneity between studies,
because similar research questions are studied in different labs,
sampling from different populations,
and using different study designs, instruments, and methods.
Any of those between-studies differences can introduce *systematic heterogeneity* in observed effect sizes.
Suspected causes of systematic heterogeneity can either be used as exclusion criteria,
or controlled for using *meta-regression* [see @lopez-lopezEstimationPredictivePower2014].
The latter approach provides an opportunity to learn which factors impact the effect size
found.
However, a limitation of meta-regression is that it requires a relatively high number of cases (studies) per parameter to obtain sufficient statistical power.
In applied meta-analyses, the number of available studies is often low [@rileyInterpretationRandomEffects2011].
This introduces a risk of overfitting,
which results in uninterpretable model parameters [@hastieElementsStatisticalLearning2009].
In extreme cases, the ratio of cases to parameters can be so low that the model is not (empirically) identified,
resulting in non-convergence [@akaikeNewLookStatistical1974].
Accounting for between-studies heterogeneity thus poses a non-trivial challenge to classic meta-analytic methods.
The present study introduces a novel method that overcomes this challenge by imposing Bayesian regularizing (LASSO and horseshoe) priors on the regression coefficients.
These priors shrink the effect of irrelevant predictors towards zero while leaving important predictors relatively unaffected.
The result is a sparse model with fewer non-zero parameters,
which benefits model convergence, reduces overfitting, and helps identify relevant between-study differences.
</span>

@@

The "curse of dimensionality" refers to the aforementioned problems that arise when the number of moderators is high relative to the number of cases [@hastieElementsStatisticalLearning2009].
It can be overcome by performing *variable selection*:
identifying a smaller subset of relevant moderators from the larger set of candidate moderators [@hastieElementsStatisticalLearning2009].
<span id = "theory">One way to perform variable selection is by relying on theory,
and selecting only moderators that should theoretically have an impact on effect size.
An important caveat is that theories that describe phenomena at the level of individual units of analysis do not necessarily generalize to the study level.
Using such theories for variable selection amounts to committing the ecological fallacy:
generalizing inferences across levels of analysis [@jargowskyEcologicalFallacy2004].
The implications of the ecological fallacy for interpreting the *results* of meta-regression have been discussed elsewhere [@bakerUnderstandingHeterogeneityMetaanalysis2009]:
For example, meta-regression may find a significant positive effect of average sample age on treatment efficacy,
even if age is uncorrelated with treatment effect within each study.
A similar problem arises when using individual level theory to select study level moderators:
If theory states that an individual's age influences their susceptibility to treatment,
that does not imply that average sample age will be a relevant moderator of study-level treatment effect in meta-regression.
For an example of study level theory,
consider the *decline effect*:
effect sizes in any given tranche of the literature tend to diminish over time [@schoolerUnpublishedResultsHide2011].
When, by coincidence, a large effect is found, it initially draws attention from the research community.
Subsequent replications then find smaller effects due to regression to the mean.
Based on the decline effect, we might hypothesize "year of publication" to be a relevant moderator of study effect sizes.
At present, few such study level theories about the drivers of heterogeneity exist, and until they are developed,
theory has limited utility for variable selection.</span>

An alternative solution is to rely on statistical methods for variable selection.
This is a focal issue in the discipline of machine learning [@hastieElementsStatisticalLearning2009].
There is precedent for the use of machine learning to perform variable selection in meta-analysis [@vanlissaSmallSampleMetaanalyses2020].
This prior work used the non-parametric *random forest* algorithm to perform variable selection.
One limitation of random forests is that non-parametric models are harder to interpret,
particularly when the readership is accustomed to linear models that describe the effect of each moderator with a single parameter.

In linear models, variable selection can be accomplished via a statistical method called  *regularization*.
Regularization shrinks small model parameters towards zero,
such that irrelevant moderators are eliminated.
Different approaches to regularization exist [@hastieElementsStatisticalLearning2009].
<span id = "lassointroduction">The present paper introduces *Bayesian Regularized Meta-Regression* (BRMA),
an algorithm that uses Bayesian regularizing priors to perform variable selection in meta-analysis.
Regularizing priors assign a high probability density to near-zero values,
which shrinks small regression coefficients towards zero, thus resulting in a sparse solution.
This manuscript discusses two shrinkage priors,
the LASSO and horseshoe prior.</span>

@@

To understand how BRMA estimates the relevant parameters and performs variable selection,
it is instructional to first review the statistical underpinnings of classical meta-analysis.
In its simplest form, meta-analysis amounts to computing a weighted average of the effect sizes.
Each effect size is assigned a weight that determines how influential it is in calculating the summary effect.
The weights are based on specific assumptions.
For example, the *fixed effect* model assumes
that each observed effect size $T_i$ is an estimate of an underlying true population effect size $\beta_0$ [@hedgesFixedRandomeffectsModels1998].
This assumption is appropriate when meta-analyzing close replication studies [@higginsReevaluationRandomeffectsMetaanalysis2009].
The only cause of heterogeneity in observed effect sizes is presumed to be sampling error, $v_i$, which is treated as known, and computed as the square of the standard error of the effect size.
Thus, for a collection of $k$ studies,
the observed effects sizes of individual studies $i$ (for $i \in [1,2, \ldots k]$) are given by:
\begin{align}
T_i &= \beta_0 + \epsilon_i\\
\text{where } \epsilon_i &\sim N(0, v_i)
\end{align}
The estimated population effect size $\hat{\beta_0}$ is then a weighted average of the observed effect sizes.
The assumption that sampling error is the only source of variance in observed effect sizes implies that studies with smaller standard errors estimate the underlying true effect size more precisely and should accrue more weight.
Therefore, fixed effect weights are simply the reciprocal of the sampling variance, $w_{i} =  \frac{1}{v_i}$.
The estimate of the true effect is a weighted average across observed effect sizes:
\begin{equation}
\hat{\beta_0} = \frac{\sum_{i=1}^k w_iT_i}{\sum_{i=1}^k w_i}
\end{equation}

The *random effects* model, by contrast, assumes that,
in addition to sampling error, true effects vary for random reasons,
and thus follow a normal distribution with mean $\beta_0$ and variance $\tau^{2}$ [@hedgesFixedRandomeffectsModels1998].
This assumption is appropriate when studies are conceptually similar but differ in small random ways [@higginsReevaluationRandomeffectsMetaanalysis2009]. 
The observed effect sizes are thus given by:
\begin{align}
T_i &= \beta_0 + \zeta_{i} + \epsilon_i\\
\text{where } \zeta_i &\sim N(0, \tau^2)\\
\text{and } \epsilon_i &\sim N(0, v_i)
\end{align}
As in the fixed effect model,
studies with smaller sampling errors are assigned more weight.
However, to account for the fact that all studies now provide some information about different regions of the distribution of true effect sizes,
the weights are attenuated in proportion to the spread of that distribution.
The random effects weights are thus given by $w_{i} =  \frac{1}{v_i + \hat{\tau}^2}$.
Whereas sampling error is still treated as known,
the between-study heterogeneity $\tau^{2}$ must be estimated.
This estimate is represented by $\hat{\tau}^{2}$.

Between-studies heterogeneity is not always random, however.
Meta-regression extends the random effects model to account for systematic sources of heterogeneity,
which are coded as moderators.
It estimates the effect of moderators on effect size,
and provides an estimate of the overall effect size and residual heterogeneity after controlling for their influence.
For example, if studies have been conducted in Europe and the Americas,
one could code a binary moderator variable called "continent".
Using meta-regression, one can then estimate either the continent-specific effect size,
or control for the difference between continents when estimating the overall average effect size.
Similarly, if studies have examined the effect of a drug at different dosages,
one could code dosage as a continuous moderator and estimate the overall effect size at average dosages,
or at a specific dosage.
The equation below describes a general model for $p$ moderators,
where $x_{1\ldots p}$ represent the moderator variables,
and $\beta_{1\ldots p}$ their regression coefficients.
Note that $\beta_0$ represents the intercept of the distribution of true effect sizes after controlling for the moderators
and the error term $\zeta_{i}$ represents residual unexplained between-studies heterogeneity.
This is a mixed-effects model; the intercept and effects of moderators are treated as fixed and the residual heterogeneity as random [@lopez-lopezEstimationPredictivePower2014]:
\begin{align}
T_i &= \beta_{0}+ \beta_{1}x_{1}+ \beta_{2}x_{2} + \ldots + \beta_{p}x_{p} + \zeta_{i} + \epsilon_i\\
\end{align}

<!--The topic of estimating the residual heterogeneity is a highly discussed one (Veroniki et al., 2016; Viechtbauer \& López-López, 2015; Panityakul et al., 2013). The ability of the estimators to predict the residual heterogeneity is influenced by different factors, such as the number of studies (Guolo \& Varin, 2017; Panityakul et al., 2013; Hardy \& Thompson, 1996) included and the sample size of the individual studies (Panityakul et al., 2013).
A third, and obvious factor, that is classified as relevant to model performance is heterogeneity among studies being meta-analysed (Kontopantelis \& Reeves, 2011; Jackson \& White, 2018). Coverage from models degrades when the residual heterogeneity increases, mostly when the amount of studies is small (Brockwell \& Gorden, 2001). Considering that all models their performance is linked to the accuracy of the estimate. According to Sidik \& Jonkman (2007), it is generally the case that the larger true between-study variance is, the more biased the estimate can be, which diminishes the performance of the method.-->
Numerous methods have been proposed to estimate meta-regression models,
the most common of which is restricted maximum likelihood [REML, @pattersonRecoveryInterblockInformation1971].
REML is an iterative method, which means that it repeatedly performs the same calculations and updates the estimated parameters until their estimates stabilize.
This estimator has low bias, which means that the average values of the parameters are close to their true values [@panityakulEstimatingResidualHeterogeneity2013].
However, this bias comes at the cost of higher variance, which means that the estimated values of a population parameter vary more from one sample to the next. 
An estimator with low bias and high variance produces results that generalize less well to new data than an estimator with high bias and low variance.
This phenomenon is known as the *bias-variance trade-off*.
Regularization increases bias to reduce variance.
A disadvantage of this trade-off is that model parameters can no longer be interpreted as straightforwardly as OLS regression coefficients.
An advantage is that the resulting model is more generalizable and makes better predictions for new data [see @hastieElementsStatisticalLearning2009].

@@

Ordinary least squares regression (OLS) estimates the model parameters by minimizing the Residual Sum of Squares (RSS) of the dependent variable.
The resulting parameter estimates perfectly describe linear relations in the present data set, but generalize less well to new data:
$$
RSS=\sum_{i=1}^{n}(y_{i} - \beta_{0} - \sum_{j=1}^{p}\beta_{j}x_{ij})^2
$$
Regularized regression biases parameter estimates towards zero by adding a penalty term to the RSS.
As an example, we will discuss the most common penalty: the sum of the absolute regression coefficients, also known as the the L1- or LASSO penalty [@hastieElementsStatisticalLearning2009].
Note that other penalties exist.
As the LASSO penalty is a function of the regression coefficients, it increases when they get bigger.
This incentivizes the optimizer to keep the regression coefficients as small as possible.
Note that the amount of regularization can be controlled by multiplying the penalty by a tuning parameter, $\lambda$.
If $\lambda$ is zero, the shrinkage penalty has no impact.
As $\lambda$ increases,
all coefficients shrink towards zero, ultimately producing the null model.
Cross-validation is often used to find the optimal value for the penalty parameter $\lambda$.
The LASSO penalized residual sum of squares is given by:
$$
PRSS= RSS + \lambda \sum_{j=1}^{p}|\beta_{j}|
$$

@@

<span id = "morepriors">An alternative to the use of a shrinkage penalty is Bayesian estimation with a regularizing prior.
Whereas the aforementioned (frequentist) approaches treat every possible parameter value as equally plausible,
Bayesian estimation combines information from the data with a *prior distribution* that assigns a-priori probability to different parameter values.
Likely parameter values have a high probability density, and unlikely parameter values have a low probability density.
The prior distribution is updated with the likelihood of the data to form a posterior distribution,
which reflects expectations about likely parameter values after having seen the data [for an extensive introduction, see @mcelreathStatisticalRethinkingBayesian2020].

A regularizing prior distribution shrinks small coefficients towards zero by assigning high probability mass to near-zero values.
There are many different regularizing prior distributions [@vanErpOberskiMulder2019].
Some of these regularizing priors are analogous to specific frequentist methods.
For example, a double exponential prior (hereafter: LASSO prior) results in posterior distributions whose modes are identical to the estimates from LASSO-penalized regression [@ParkCasella2008].
There are some notable differences between the frequentist LASSO penalty and its Bayesian counterpart, the LASSO prior. First, the frequentist LASSO penalty has a tuning parameter $\lambda$, whose value is usually chosen via cross-validation. 
In the Bayesian approach, an analogous role is fulfilled by a hyperparameter of the shrinkage prior.
Instead of using cross-validation, the value of this hyperparameter can be estimated from the data.

<span id = "horseshoe">One limitation of the LASSO prior is that it biases all regression coefficients towards zero - for relevant as well as irrelevant moderators.
To overcome this limitation, regularizing priors with better shrinkage properties have been developed.
These priors still pull small regression coefficients towards zero,
but exert less bias on larger regression coefficients.
One example is the horseshoe prior [@CarvalhoPolsonScott2010].
It has heavier tails than the LASSO prior,
which means that it does not shrink (and therefore bias) substantial coefficients as much.
One remaining limitation of the horseshoe prior is that it is difficult to specify a prior that ensures a sufficiently sparse solution.
The regularizing horseshoe was introduced to overcome this limitation;
it uses information about the expected number of parameters to determine an appropriate shrinkage prior  [@PiironenVehtari2017b].</span></span>

The BRMA method introduced here offers both LASSO and regularizing horseshoe priors.
The LASSO prior is given by:
$$
\beta_{j} \sim \text{DE}(0, \frac{s}{\lambda})
$$
where DE denotes the double exponential distribution with a location equal to 0 and a scale determined by a global scale parameter $s$ and an inverse-tuning parameter $\lambda$.
In the present study, the global scale parameter is set to 1,
and the inverse-tuning parameter is assigned a $\chi^2$ prior distribution with 1 degree of freedom.
Its value is thus optimized during model estimation.

>>>>

author:
  - name: "Caspar J. Van Lissa"
    affiliation: "1"
    corresponding: yes
    address: "Professor Cobbenhagenlaan 125, 5037 DB Tilburg, The Netherlands"
    email: "c.j.vanlissa@tilburguniversity.edu"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Formal Analysis
      - Funding acquisition
      - Methodology
      - Project administration
      - Software
      - Supervision
      - Writing – original draft
      - Writing – review & editing
  - name: "Sara van Erp"
    affiliation: "2"
    role:
      - Methodology
      - Software
      - Writing – original draft
      - Writing – review & editing
  - name: "Eli-Boaz Clapper"
    affiliation: "2"
    role:
      - Formal Analysis
      - Writing – original draft
      - Writing – review & editing
affiliation:
  - id            : "1"
    institution   : "Tilburg University, dept. Methodology & Statistics"
  - id            : "2"
    institution   : "Utrecht University, dept. Methodology & Statistics"

@@

abstract: |
  When meta-analyzing heterogeneous bodies of literature,
  meta-regression can be used to account for potentially relevant between-studies differences.
  A key challenge is that the number of candidate moderators is often high
  relative to the number of studies.
  This introduces risks of overfitting, spurious results, and model non-convergence.
  To overcome these challenges,
  <span id = "lassoabstract">we introduce Bayesian Regularized
  Meta-Analysis (BRMA),
  which selects relevant moderators from a larger set of candidates
  by shrinking small regression coefficients towards zero
  with regularizing (LASSO or horseshoe) priors.</span>
  This method is suitable when there are many potential moderators,
  but it is not known beforehand which of them are relevant.
  A simulation study compared BRMA against state-of-the-art random effects
  meta-regression using restricted maximum likelihood (RMA).
  Results indicated that BRMA outperformed RMA on three metrics:
  BRMA had superior predictive performance, which means that the results
  generalized better;
  BRMA was better at rejecting irrelevant moderators,
  and worse at detecting true effects of relevant
  moderators,
  while the overall proportion of Type I and Type II errors was
  equivalent to RMA.
  BRMA regression coefficients were slightly biased towards zero (by design),
  but its residual heterogeneity estimates were less biased than those of RMA.
  BRMA performed well with as few as 20 studies,
  suggesting its suitability as a small sample solution. 
  We present free open source software implementations in the R-package `pema` (for penalized meta-analysis)
  and in the stand-alone statistical program JASP.
  An applied example demonstrates the use of the R-package.

@@

bibliography      : ["meta-analysis.bib"]

@@

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed, warning = FALSE, message = FALSE)
```

@@

<span id = "openingparagraph">A common application of meta-analysis is to summarize existing bodies of literature.
A crucial challenge is that there is often substantial heterogeneity between studies,
because similar research questions are studied in different labs,
sampling from different populations,
and using different study designs, instruments, and methods.
Any of those between-studies differences can introduce *systematic heterogeneity* in observed effect sizes.
Suspected causes of systematic heterogeneity can either be used as exclusion criteria,
or controlled for using *meta-regression* [see @lopez-lopezEstimationPredictivePower2014].
The latter approach provides an opportunity to learn which factors impact the effect size
found.
However, a limitation of meta-regression is that it requires a relatively high number of cases (studies) per parameter to obtain sufficient statistical power.
In applied meta-analyses, the number of available studies is often low [@rileyInterpretationRandomEffects2011].
This introduces a risk of overfitting,
which results in uninterpretable model parameters [@hastieElementsStatisticalLearning2009].
In extreme cases, the ratio of cases to parameters can be so low that the model is not (empirically) identified,
resulting in non-convergence [@akaikeNewLookStatistical1974].
Accounting for between-studies heterogeneity thus poses a non-trivial challenge to classic meta-analytic methods.
The risk of arriving at false-positive conclusions
when there are many potential moderators is so ubiquitous that it was referred to as the "primary pitfall" in meta-regression [@thompsonHowShouldMetaregression2002].
The present study introduces a novel method to overcome this pitfall by imposing Bayesian regularizing (LASSO and regularizing horseshoe) priors on the regression coefficients.
These priors shrink the effect of irrelevant predictors towards zero while leaving important predictors relatively unaffected.
The result is a sparse model with fewer non-zero parameters,
which benefits model convergence, reduces overfitting, and helps identify relevant between-study differences.
</span>

@@

The "curse of dimensionality" refers to the aforementioned problems that arise when the number of moderators is high relative to the number of cases [@hastieElementsStatisticalLearning2009].
It can be overcome by performing *variable selection*:
identifying a smaller subset of relevant moderators from the larger set of candidate moderators [@hastieElementsStatisticalLearning2009].
<span id = "theory">Prior authors have stressed the need to perform variable selection in meta-regression,
for example, by limiting the number of moderators considered [@thompsonHowShouldMetaregression2002].
This does not resolve the problem, however,
as failing to consider a moderator does not mean that it is irrelevant.
Instead, moderators ought to be selected based on their theoretical or empirical relevance for the studied effect.

One approach to is to select variables on theoretical grounds.
An important caveat is that theories that describe phenomena at the level of individual units of analysis do not necessarily generalize to the study level.
Using such theories for variable selection amounts to committing the ecological fallacy:
generalizing inferences across levels of analysis [@jargowskyEcologicalFallacy2004].
The implications of the ecological fallacy for interpreting the *results* of meta-regression are well-known [@bakerUnderstandingHeterogeneityMetaanalysis2009; @thompsonHowShouldMetaregression2002]:
For example, meta-regression may find a significant positive effect of average sample age on the effect size of a randomized controlled trial,
even if age is uncorrelated with treatment efficacy within each study.
Less well-known is that the same problem applies when using individual level theory to select study level moderators:
If theory states that an individual's age influences their susceptibility to treatment,
that does not imply that average sample age will be a relevant moderator of study-level treatment effect in meta-regression.
One rare example of study level theory is the *decline effect*:
effect sizes in any given tranche of the literature tend to diminish over time [@schoolerUnpublishedResultsHide2011].
When, by coincidence, a large effect is found, it initially draws attention from the research community.
Subsequent replications then find smaller effects due to regression to the mean.
Based on the decline effect, we might hypothesize "year of publication" to be a relevant moderator of study effect sizes.
At present, few such study level theories about the drivers of heterogeneity exist, and until they are developed,
theory has limited utility for variable selection.</span>
A further complication is that theoretically relevant variables might not be reported in many published papers,
which may be one reason why moderator analyses are rarely executed as planned [@thompsonHowShouldMetaregression2002]

An alternative solution is data-driven variable selection using appropriate statistical techniques.
This is a focal issue in the discipline of machine learning [@hastieElementsStatisticalLearning2009].
There is precedent for the use of machine learning for variable selection in meta-analysis [@vanlissaSmallSampleMetaanalyses2020].
This prior work used the non-parametric *random forest* algorithm.
A limitation of random forests is that its results are harder to interpret than linear models,
which describe the effect of each moderator with a single parameter.
The present study instead uses *regularization*,
which is a method for variable selection in linear models.
Regularization shrinks small model parameters towards zero,
such that irrelevant moderators are eliminated.
Different approaches to regularization exist [@hastieElementsStatisticalLearning2009].
<span id = "lassointroduction">The present paper introduces *Bayesian Regularized Meta-Regression* (BRMA),
an algorithm that uses Bayesian regularizing priors to perform variable selection in meta-analysis.
Regularizing priors assign a high probability density to near-zero values,
which shrinks small regression coefficients towards zero, thus resulting in a sparse solution.
This manuscript discusses two shrinkage priors,
the LASSO and regularizing horseshoe prior.</span>

@@

To understand how BRMA estimates the relevant parameters and performs variable selection,
it is instructional to first review the statistical underpinnings of classical meta-analysis.
In its simplest form, meta-analysis amounts to computing a weighted average of the effect sizes.
Each effect size is assigned a weight that determines how influential it is in calculating the summary effect.
The weights are based on specific assumptions.
For example, the *fixed effect* model assumes
that each observed effect size $T_i$ is an estimate of an underlying true population effect size $\beta_0$ [@hedgesFixedRandomeffectsModels1998].
This assumption is appropriate when meta-analyzing close replication studies [@higginsReevaluationRandomeffectsMetaanalysis2009a].
The only cause of heterogeneity in observed effect sizes is presumed to be sampling error, $v_i$, which is treated as known, and computed as the square of the standard error of the effect size.
Thus, for a collection of $k$ studies,
the observed effects sizes of individual studies $i$ (for $i \in [1,2, \ldots k]$) are given by:
\begin{align}
T_i &= \beta_0 + \epsilon_i\\
\text{where } \epsilon_i &\sim N(0, v_i)
\end{align}
The estimated population effect size $\hat{\beta_0}$ is then a weighted average of the observed effect sizes.
The assumption that sampling error is the only source of variance in observed effect sizes implies that studies with smaller standard errors estimate the underlying true effect size more precisely and should accrue more weight.
Therefore, fixed effect weights are simply the reciprocal of the sampling variance, $w_{i} =  \frac{1}{v_i}$.
The estimate of the true effect is a weighted average across observed effect sizes:
\begin{equation}
\hat{\beta_0} = \frac{\sum_{i=1}^k w_iT_i}{\sum_{i=1}^k w_i}
\end{equation}

The *random effects* model, by contrast, assumes that,
in addition to sampling error, true effects vary for random reasons,
and thus follow a normal distribution with mean $\beta_0$ and variance $\tau^{2}$ [@hedgesFixedRandomeffectsModels1998].
This assumption is appropriate when studies are conceptually similar but differ in small random ways [@higginsReevaluationRandomeffectsMetaanalysis2009a]. 
The observed effect sizes are thus given by:
\begin{align}
T_i &= \beta_0 + \zeta_{i} + \epsilon_i\\
\text{where } \zeta_i &\sim N(0, \tau^2)\\
\text{and } \epsilon_i &\sim N(0, v_i)
\end{align}
In this model, the error term $\zeta_{i}$ represents between-studies heterogeneity, with variance $\tau^2$.
As in the fixed effect model,
studies with smaller sampling errors are assigned more weight.
<span id = "informationdistribution">In contrast to the fixed effect model, the random effects model assumes that all studies provide some information about the underlying distribution of true effect sizes.
Fixed effect weights would discount the information smaller studies provide about the scale of this distribution, which is represented by it's variance $\tau^2$.
To overcome this limitation, the weights are attenuated in proportion to the variance.
The random effects weights are thus given by $w_{i} =  \frac{1}{v_i + \hat{\tau}^2}$.</span>
Whereas sampling error is still treated as known,
the between-study heterogeneity $\tau^{2}$ must be estimated.
This estimate is represented by $\hat{\tau}^{2}$.

Between-studies heterogeneity is not always random, however.
Meta-regression extends the random effects model to account for systematic sources of heterogeneity,
which are coded as moderators.
It estimates the effect of moderators on effect size,
and provides an estimate of the overall effect size and residual heterogeneity after controlling for their influence.
For example, if studies have been conducted in Europe and the Americas,
one could code a binary moderator variable called "continent".
Using meta-regression, one can then estimate either the continent-specific effect size,
or control for the difference between continents when estimating the overall average effect size.
Similarly, if studies have examined the effect of a drug at different dosages,
one could code dosage as a continuous moderator and estimate the overall effect size at average dosages,
or at a specific dosage.
The equation below describes a general model for $p$ moderators,
where $x_{1\ldots p}$ represent the moderator variables,
and $\beta_{1\ldots p}$ their regression coefficients.
Note that $\beta_0$ now represents the intercept of the distribution of true effect sizes after controlling for the moderators.
This is a mixed-effects model; the intercept and effects of moderators are treated as fixed and the residual heterogeneity as random [@lopez-lopezEstimationPredictivePower2014]:
\begin{align}
T_i &= \beta_{0}+ \beta_{1}x_{1}+ \beta_{2}x_{2} + \ldots + \beta_{p}x_{p} + \zeta_{i} + \epsilon_i
\end{align}

@@

Meta-regression models are most commonly estimated using weighted least squares,
with weights determined according to the aforementioned random effects model,
where residual heterogeneity is estimated using restricted maximum likelihood [@pattersonRecoveryInterblockInformation1971; @viechtbauerBiasEfficiencyMetaAnalytic2005].
This approach, henceforth referred to as RMA, has low bias, which means that, across hypothetical replications of a study, the average values of model parameters are close to their true population values [@panityakulEstimatingResidualHeterogeneity2013].
Low bias comes at the cost of higher variance, however,
which means that the estimated values of population parameters vary more from one hypothetical replication to the next.
This phenomenon is known as the *bias-variance trade-off*.
In general, an estimator with low bias and high variance produces results that generalize less well to new data than an estimator with high bias and low variance.
Regularized approaches to regression intentionally increase bias in order to reduce variance.
This is a sensible approach in the context of small samples, which are common in meta-analyses,
because small samples incur a high risk of overfitting,
and typically have relatively high levels of multicollinearity,
due to the higher probability that extreme values on one moderator coincide with extreme values on another.
In such cases, regularized regression reduces the risk of overfitting and increase generalizability of the results [see @hastieElementsStatisticalLearning2009].

<span id = "reftibshirani">To understand how regularized regression introduces bias, consider a comparison between ordinary least squares regression and LASSO regression [for a more elaborate introduction, see @tibshiraniRegressionShrinkageSelection2011].</span>
Ordinary least squares regression (OLS) estimates model parameters by minimizing the Residual Sum of Squares (RSS) of the outcome variable, given by the formula below.
In this equation, $n$ is the number of participants; $y_i$ is the outcome variable, and $x$ is one of $p$ predictor variables.
\begin{align}
RSS=\sum_{i=1}^{n}(y_{i} - \beta_{0} - \sum_{j=1}^{p}\beta_{j}x_{ij})^2
\end{align}
The resulting parameter estimates perfectly describe linear relations in the present data set, but generalize less well to new data.
Regularized regression biases parameter estimates towards zero by adding a penalty term to the RSS.
Most common is the LASSO penalty, which consists of the sum of the absolute regression coefficients, or the L1 norm [@hastieElementsStatisticalLearning2009].
As the LASSO penalty is a function of the regression coefficients, it increases when they get bigger.
This incentivizes the optimizer to keep the regression coefficients as small as possible.
The amount of regularization can be controlled by multiplying the penalty by a tuning parameter, $\lambda$.
If $\lambda$ is zero, the shrinkage penalty has no impact.
As $\lambda$ increases,
all coefficients shrink towards zero, ultimately producing the null model.
Cross-validation is often used to find the optimal value for the penalty parameter $\lambda$.
The LASSO penalized residual sum of squares is given by:
\begin{align}
PRSS= RSS + \lambda \sum_{j=1}^{p}|\beta_{j}|
\end{align}
<span id = "whylasso">Note that many other regularizing penalties exist.
This introduction focuses on the LASSO penalty because it is most ubiquitous, easy to understand,
and has an analogue in Bayesian estimation,
as explained in the next section.</span>

<span id = "earlierpapers">Some seminal studies have applied the LASSO to perform moderator selection in meta-regression [@rosettieCosteffectivenessHPVVaccination2021; @sebriNaturalResourcesIncome2021; @requiaGlobalAssociationAir2018].
This suggests that others have recognized its potential for exploring heterogeneity when the number of moderators is relatively high to the number of studies.
However, these existing publications have taken a two-step approach, whereby moderators are first selected using LASSO regression,
and selected moderators are then included in meta-regression analysis.
This approach is fraught; firstly, because of known problems of inference after variable selection [@zhangInferenceVariableSelection1992].
As the moderators included in the second step are based on an exploratory first step,
their parameters are not valid for inference.
Secondly, although the LASSO model in the first step accounts for potential multicollinearity by including all colinear variables but restricting the size of their coefficients,
the meta-regression in the second step no longer does so.
A three-step extension of the two-step approach exists
that uses principles from the causal inference literature to overcome these limitations [@belloniInferenceTreatmentEffects2014].
BRMA, by contrast, overcomes these limitations by introducing a one-step approach that performs inference within the penalized framework.</span>

@@

<span id = "morepriors">An alternative to the use of a shrinkage penalty is Bayesian estimation with a regularizing prior.
Whereas the aforementioned (frequentist) approaches treat every possible parameter value as equally plausible,
Bayesian estimation combines information from the data with a *prior distribution* that assigns a-priori probability to different parameter values.
Likely parameter values have a high probability density, and unlikely parameter values have a low probability density.
The prior distribution is updated with the likelihood of the data to form a posterior distribution,
which reflects expectations about likely parameter values after having seen the data.
<span id = "refmcelreath">For a more extensive introduction to Bayesian estimation, see @mcelreathStatisticalRethinkingBayesian2020.</span>

A regularizing prior distribution shrinks small coefficients towards zero by assigning high probability mass to near-zero values.
There are many different regularizing prior distributions,
some of which are analogous to specific frequentist methods [@vanErpOberskiMulder2019].
For example, a double exponential prior (hereafter: LASSO prior) results in posterior distributions whose modes are identical to the estimates from LASSO-penalized regression [@ParkCasella2008].
Both the the frequentist LASSO penalty and the Bayesian LASSO prior have a tuning parameter $\lambda$ that controls the amount of regularization.
In frequentist LASSO, its value is usually chosen via cross-validation [@hastieElementsStatisticalLearning2009]. 
In the Bayesian approach, by contrast,
its value can be optimized during model estimation.

<span id = "horseshoe">One limitation of the LASSO prior is that it biases all regression coefficients towards zero - for relevant as well as irrelevant moderators.
To overcome this limitation, regularizing priors with better shrinkage properties have been developed.
These priors still pull small regression coefficients towards zero,
but exert less bias on larger regression coefficients.
One example is the horseshoe prior [@CarvalhoPolsonScott2010].
It has heavier tails than the LASSO prior,
which means that it does not shrink (and therefore bias) substantial coefficients as much.
One limitation of the horseshoe prior is that it is difficult to specify a prior that ensures a sufficiently sparse solution.
The regularizing horseshoe was introduced to overcome this limitation [@PiironenVehtari2017b].</span></span>

The BRMA method introduced here offers both LASSO and regularizing horseshoe priors.
The LASSO prior is given by:
\begin{align}
\beta_{j} &\sim \text{DE}(0, \frac{s}{\lambda})\\ (\#eq:lasso)
\lambda &\sim \chi^2(0, \nu_1)
\end{align}
where DE denotes the double exponential distribution centered around zero,
with a scale determined by a global scale parameter $s$ that is multiplied by the inverse of tuning parameter $\lambda$.
Increasing the scale parameter extends the prior to cover more extreme values.
The inverse tuning parameter is estimated from the data 
by assigning it a $\chi^2$ prior distribution with mean zero and degrees of freedom $\nu_1$ [@vanErpOberskiMulder2019].
Increasing the degrees of freedom assigns greater probability mass to extreme values, resulting in less regularization.
The present study used default values for the prior parameters,
$s = 1$, $\nu_1 = 1$, as suggested by @vanErpOberskiMulder2019.
